### 2014-12-11 paper.tex
my section of the methods section

  When people think of measuring gerrymandering, the first kind of metric that comes to mind is generally one that tries to measure the compactness of a district.  In fact, there are a number of ways of measuring compactness; some are better than others, but many measure different types of compactness.  There are three major types: those that measure the dispersion of the district from its center, those that measure some form of boundary complexity, and those that are based on population and population density.

@@

@@

  %TODO: Miriam fill in convex hull and circumscribed circle metrics here.
  %TODO: possibly reorganize this subsection once Miriam adds her parts

@@

  Overall, the voter share/seat share metric is much easier to calculate, as nothing needs to be known about the individual districts, but rather only the totals of the overall election.  However, as we will expose in the analysis and discussion sections, the assumption that all districts have the same total votes does not hold well due to turnout variance and creates issues when analyzing the data.\\

@@

  \subsection{Court Test Threshold}
  10\% for areas w/at least 3 districts, include compactness considerations.  if close on one, consider the other
  \subsection{Policy Recommendations}
  Use nonpartisan methods

>>>>

  When people think of measuring gerrymandering, the first kind of metric that comes to mind is generally one that tries to measure the compactness of a district.  In fact, there are a number of ways of measuring compactness; some are better than others, but many measure different types of compactness.  There are three major types: those that measure the dispersion of the district from its center, those that measure some form of boundary complexity, and those that are based on population and population density.
% TODO: maybe this wants a figure to show some of the metrics visually? At least convex hull probably wants this, maybe also circumscribing/inscribed circle although those matter less since we never computed them. Also, is ``areal center of mass'' a word I haven't heard before or a typo?

@@

  Another purely geometric computation that we ran was the ratio of district area to area inside the convex hull of the district. For non-contiguous districts, which generally include islands, we simply computed one convex hull encompassing the entire district rather than trying to handle different sections separately. This results in some situations where a district is penalized for having a large area of water outside the district boundary. However, the alternative would fail to catch cases where a populated island is assigned to a district in an unreasonable way. Since both options have their drawbacks, we chose the one that simplified computation.

@@

  The ratio of district population to population inside the convex hull of the district introduced another issue: determining population inside an arbitrary area. The available population data was by census block, so we had to compute which census blocks are inside each convex hull. We chose to count a census block as being ``inside'' the convex hull if the interior of the census block and the interior of the convex hull overlap. We ignored census blocks outside of the state that the district is in, even if those blocks might be inside the convex hull, since they are irrelevant for redistricting purposes and it is ideal to avoid penalizing states which are themselves not compact.

  %TODO: possibly reorganize this subsection once Miriam adds her parts

@@

  Overall, the voter share/seat share metric is much easier to calculate, as nothing needs to be known about the individual districts, but rather the totals of the overall election.  However, as we will expose in the analysis and discussion sections, the assumption that all districts have the same total votes is wrong due to turnout variance and creates issues when analyzing the data.\\

@@

  \subsection{Court Test Threshold}
  10\% for areas w/at least 3 districts
  \subsection{Policy Recommendations}
  Use nonpartisan methods
